Outpacing the Lanes: Toronto's Bike Share Ridership Surges Ahead of Infrastructure Growth

### 2024-09-25 paper/paper.qmd
Created data simulation and testing. Testing revealed errors in my data cleanining script, which is now fixed.

bikeShare_data <- read_csv(here::here(
  "data/analysis_data/monthly_aggregated_bikeshare_data.csv"))
bikeShare_data <- bikeShare_data %>% filter(year(start_date) <= 2023)

bikeWay_data <- read_csv(here::here("data/analysis_data/bikeway_data.csv"))
bikeWay_data <- bikeWay_data %>% filter(INSTALLED <= 2023)

>>>>

bikeShare_data <- read_csv(here::here(
  "data/analysis_data/monthly_aggregated_bikeshare_data.csv"))

bikeWay_data <- read_csv(here::here("data/analysis_data/bikeway_data.csv"))
